---
output: github_document
---
 
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-4.2.0-6666ff.svg)](https://cran.r-project.org/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)

---

## **pseudoCure**

----

```{r, echo = FALSE}
knitr::opts_chunk$set(comment = NA, prompt = TRUE, collapse = TRUE)
```

## pseudoCure: Analysis of survival data with cure fraction and variable selection: A pseudo-observations approach


The __pseudoCure__ package implements a pseudo-observation approach for survival data with a cure fraction.
The modeling framework is based on the Cox proportional hazards mixture cure model and
the bounded cumulative hazard model.


## Installation

The package will be available on CRAN soon.
Install and load the package from GitHub using 
```{r github, eval = FALSE}
devtools::install_github("stc04003/pseudoCure")
library(pseudoCure)
packageVersion("pseudoCure")
```

## Reference 

Su, C.-L., Chiou, S., Lin, F.-C., and Platt, R. W. (2022)
Analysis of survival data with cure fraction and variable selection: A pseudo-observations approach
*Statistical Methods in Medical Research*, **31**(11): 2037--2053.
